---
title: "1-preparation"
author: "bernard-liew"
date: "2020-06-11"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Load library 

```{r message=FALSE, warning=FALSE}

# Helper packages
library (tidyverse)
library (tidyselect)
library (arsenal)
library (janitor)
library (magrittr)

# Import
library(readxl)
library (xlsx)

# Statistics
library (mice)
library (VIM)
library (corrr)


```

# Import data

```{r}

rm (list = ls())
dat <-  read_excel("data/stops_dat.xlsx", 
    sheet = "data")

dat <- dat[c(1:300),]

cnames <- names (dat)
cnames_mod <- str_replace_all (tolower(cnames), 
                                           pattern = " ", 
                                           repl = "_")
names (dat) <- cnames_mod 

df_orig <- dat

```

# Tidy data

## Remove dummary variables

```{r}

dummy_var <- grep ("dummy|0,|v_", cnames_mod, value = TRUE)

dat_sub <- dat[, !names (dat) %in% dummy_var]

(ncol (dat_sub) + length (dummy_var)) == length (names (dat))

df_orig_sub <- dat_sub

```

## Group variables 

```{r}

cnames_mod <- names (dat_sub)

# Time related variables

base_var <- grep ("baseline", cnames_mod, value = TRUE)

wk5_var <- grep ("5week|5_week", cnames_mod, value = TRUE)

wk10_var <- grep ("10week|10_week", cnames_mod, value = TRUE)

wk26_var <- grep ("26week|26_week", cnames_mod, value = TRUE)

wk52_var <- grep ("52week|52_week", cnames_mod, value = TRUE)

# Baseline variables

id_var<- tidyselect::vars_select (cnames_mod, 
                                          c("stops_id":
                                              "baseline_date"))

orebro_var <- grep ("orebro", cnames_mod, value = TRUE)

fab_var <- grep ("fab", cnames_mod, value = TRUE)

work_var <- grep ("work|industry|occupation", cnames_mod, value = TRUE)

symptom_var <- grep ("symptom|next", cnames_mod, value = TRUE)

symptomLoc_var <- grep ("location", cnames_mod, value = TRUE)

episode_var <- grep ("episode", cnames_mod, value = TRUE)

sfbs_var <- grep ("sfbs", cnames_mod, value = TRUE)

other_var <- grep ("other_rx", cnames_mod, value = TRUE) # remove

treatment_var <- tidyselect::vars_select (cnames_mod, 
                                          c("treatment:_number_of_practitioners_seen_(all)":
                                              "10:_rest_of_life"))

meds_var <- tidyselect::vars_select (cnames_mod, c("paracetamol":
                                                     "medication:_number_of_med_types_(all)")) # remove



misc_var <-  tidyselect::vars_select (cnames_mod, 
                                          c("weight_(kg)":
                                              "sa1_(code)"))

ses_var <- grep ("ses:", cnames_mod, value = TRUE)

personal_var <-  tidyselect::vars_select (cnames_mod, 
                                          c("highest_level_of_education":
                                              "number_of_smokes...316"))

symptHx_var <-  tidyselect::vars_select (cnames_mod, 
                                          c("have_you_taken_any_tablets_for_your_back_today?":
                                              "if_you_have_leg_and_back_symptoms,_are_they_related?...338"))


aggr_var <-  grep ("agg|difficult|sorer", cnames_mod, value = TRUE)

ease_var <-  grep ("ease|comfortable", cnames_mod, value = TRUE)

obj_curve_var <- tidyselect::vars_select (cnames_mod, 
                                          c("assessment:_obs:_standing-increased_lordosis":
                                              "list_corresponding_to_worst_side"))

obj_rom_var <- tidyselect::vars_select (cnames_mod, 
                                          c("amt:_flexion_range_(cm)...462":
                                              "range_of_side_with_most_limited_lf"))

obj_core_var <- tidyselect::vars_select (cnames_mod, 
                                          c("core_stability_in_standing":
                                              "ta_low_tone"))

obj_sit_var <- grep ("sitting:", cnames_mod, value = TRUE)

obj_neuro_var <- tidyselect::vars_select (cnames_mod, 
                                          c("positive_slr":
                                            "clinical_radiculopathy_with_no_mechanical_cause_on_imaging"))

aggr2_var <-  tidyselect::vars_select (cnames_mod, 
                                          c("oswestry:_sitting_(p3)":
                                              "repeated_movements:_reducible?"))

obj_core2_var <- grep ("multifidus", cnames_mod, value = TRUE)

obj_disc_var <- tidyselect::vars_select (cnames_mod, 
                                          c("regular_compression":
                                            "degree_of_nerve_contact"))

redflag_var <- tidyselect::vars_select (cnames_mod, 
                                          c("constant_symptoms":
                                            "general_health_state"))

euroqol_var <- grep ("euroqol", cnames_mod, value = TRUE)

```


## Rename variables

### Baseline outcome variables

```{r}

dat_base_var <- dat_sub[, names (dat_sub) %in% base_var]
dat_base_var <- dat_base_var[, !names (dat_base_var) %in% c ("baseline_date",
                                                             "baseline_time_(0_weeks)",
                                                             "baseline_pain_(leg)...9")]
dat_base_var $working_at_baseline <- NULL
new.name1 <- paste0("base_", c ("osw",
                                 "lbp",
                                 "lp"))  
new.name2 <- paste0 ("base_osw_q", c(1:10))

names(dat_base_var) <- c(new.name1, new.name2)
  
```

### Week 5 outcome variables

```{r}

dat_wk5_var <- dat_sub [, names (dat_sub) %in% wk5_var]
dat_wk5_var  <- dat_wk5_var [, !names (dat_wk5_var) %in% c ("5_week_outcome_date", 
                                                            "5_weeks_(days_since_om_completed)",
                                                            "5_weeks_(weeks_since_om_completed)")]

new.name1 <- paste0("wk5_", c ("osw",
                               "lbp",
                               "lp",
                               "oreb"))  
new.name2 <- paste0 ("wk5_oreb_q", c(4:24))

names(dat_wk5_var) <- c(new.name1, new.name2)
  
```

### Week 10 outcome variables

```{r}

dat_wk10_var <- dat_sub [, names (dat_sub) %in% wk10_var]
dat_wk10_var  <- dat_wk10_var [, !names (dat_wk10_var) %in% c ("10_week_outcome_date", 
                                                            "10_weeks_(days_since_om_completed)",
                                                            "10_weeks_(weeks_since_om_completed)")]

new.name1 <- paste0("wk10_", c ("osw",
                               "lbp",
                               "lp",
                               "oreb"))  
new.name2 <- paste0 ("wk10_oreb_q", c(4:24))

names(dat_wk10_var) <- c(new.name1, new.name2)
  
```

### Week 26 outcome variables

```{r}

dat_wk26_var <- dat_sub [, names (dat_sub) %in% wk26_var]
dat_wk26_var  <- dat_wk26_var [, !names (dat_wk26_var) %in% c ("26_week_outcome_date", 
                                                            "26_weeks_(days_since_om_completed)",
                                                            "26_weeks_(weeks_since_om_completed)")]

new.name1 <- paste0("wk26_", c ("osw",
                               "lbp",
                               "lp",
                               "oreb"))  
new.name2 <- paste0 ("wk26_oreb_q", c(4:24))

names(dat_wk26_var) <- c(new.name1, new.name2)
  
```

### Week 52 outcome variables

```{r}

dat_wk52_var <- dat_sub [, names (dat_sub) %in% wk52_var]
dat_wk52_var  <- dat_wk52_var [, !names (dat_wk52_var) %in% c ("52_week_outcome_date", 
                                                            "52_weeks_(days_since_om_completed)",
                                                            "52_weeks_(weeks_since_om_completed)")]

new.name1 <- paste0("wk52_", c ("osw",
                               "lbp",
                               "lp",
                               "oreb"))  
new.name2 <- paste0 ("wk52_oreb_q", c(4:24))

names(dat_wk52_var) <- c(new.name1, new.name2)
  
```

### Baseline id variables

```{r}

dat_id_var <- dat_sub [, names (dat_sub) %in% id_var]
dat_id_var  <- dat_id_var [, !names (dat_id_var) %in% c ("baseline_date")]

names(dat_id_var) <- c("id", "rx_grp", "rx_subgrp")
  
```


### Baseline orebro

```{r}

orebro_var_sub <- orebro_var[!grepl("5w|10w|26w|52w|...37", orebro_var)]

dat_orebro_var <- dat_sub [, names (dat_sub) %in% orebro_var_sub ]

new.name1 <- c("base_oreb", paste0 ("base_oreb_q", c(4:24)))

names(dat_orebro_var) <- new.name1  

```

### Baseline fab

```{r}

dat_fab_var <- dat_sub [, names (dat_sub) %in% fab_var]

names(dat_fab_var) <- "base_fab"  

```

### Baseline work

```{r}

work_var2 <- tidyselect::vars_select (work_var, 
                                          -c("19:_reason_pre-injury_work_status...64":
                                            "working_other_than_nd_due_to_current__lbp",
                                            "pre-inj_workers'_perceived_chance_of_working_at_6/12...72",
                                            "workers'_perception_of_heavy_or_monotonous_work...75" ,
                                            "pre-injury_workers'_sick_leave_duration_due_to_pain...78",
                            "pre-injury_house-keepers'_or_workers'_sick_leave_duration_due_to_pain...81",
                            "pre-injury_house-keepers'_or_workers'_sick_leave_duration_due_to_pain...80",
                            "ses:_index_of_education_and_occupation" ,
                             "occupation" ))

dat_work_var <- dat_sub [, names (dat_sub) %in% work_var2]


new.name1 <- c("work_status", "work_duty", "reas_not_work", "pre_work_status",
               "pre_work_duty", "reas_pre_work_status", "pre_perc_work6mth",
               "work", "prec_work", "work_statifac", "pre_sickleave_pain",
               "pain_interfer",  "industry", "hx_heavywork")

new.name2 <- paste0 ("base_", new.name1)

names(dat_work_var) <- new.name2  

```

### Baseline symptoms

```{r}

symptom_var2 <- tidyselect::vars_select (symptom_var , 
                                          -c("duration_of_leg_symptoms...100":
                                            "duration_of_symptoms:_longest_lx_or_leg" ,
                                            "if_you_have_leg_and_back_symptoms,_are_they_related?...337",
                                            "first_time_symptoms_started...422",
                                            "time_of_day_symptoms_came_on...428",
                                            "how_next_day...434" ,
                                            "symptoms_following_day_much_worse_(p25)",
                                            "constant_symptoms",
                                            "night_symptoms" ))

dat_symptom_var <- dat_sub [, names (dat_sub) %in% symptom_var2 ]


new.name1 <- c("lbp_symptom", "leg_symptom", "lbp_duration", "leg_duration",
               "freq_symptom", "back_leg_relation", "onset_symptom",
               "time_symptom", "next_day_symptom", "pain_side")

new.name2 <- paste0 ("base_", new.name1)

names(dat_symptom_var) <- new.name2  

```

### Baseline symptom location

```{r}

symptomLoc_var2 <- tidyselect::vars_select (symptomLoc_var , 
                                          -c("pain_location:_body_chart_-_psych...96",
                                            "pain_location:_body_chart_-_psych...97",
                                            "duration_of_leg_symptoms+pain_location_(body_chart)"))

dat_symptomLoc_var <- dat_sub [, names (dat_sub) %in% symptomLoc_var2]


new.name1 <- c("loc_antthigh_pain", "loc_belowknee_pain", "loc_leg_pain", "loc_body_ratio",
               "loc_mostpain")

new.name2 <- paste0 ("base_", new.name1)

names(dat_symptomLoc_var) <- new.name2  

```

### Baseline episode

```{r}

episode_var2 <- tidyselect::vars_select (episode_var , 
                                          -c( "previous_lbp_episodes:_<=4,_>4,_n_appl"  ,
                                             "not_the_first_ep_and_previous_lbp_episodes:_<=4,_>4,_n_appl"))

dat_episode_var <- dat_sub [, names (dat_sub) %in% episode_var2]


new.name1 <- c("first_episode", "first_episode_period")

new.name2 <- paste0 ("base_", new.name1)

names(dat_episode_var ) <- new.name2  

```


### Baseline sfbs

```{r}

dat_sfbs_var <- dat_sub [, names (dat_sub) %in% sfbs_var]


new.name1 <- c("freq_1", "freq_2", "freq_3", "freq_4", "freq_5",
               "sciatica_freq_lbp", "sciatica_freq_nolbp", "bother_1",
               "bother_2", "bother_3", "bother_4", "bother_5",
               "sciatica_bother_lbp", "sciatica_bother_nolbp")

new.name2 <- paste0 ("base_sfbs_", new.name1)

names(dat_sfbs_var) <- new.name2  

```

### Baseline other

```{r}

dat_other_var <- dat_sub [, names (dat_sub) %in% other_var]


```


### Baseline treatment

```{r}


treatment_var2 <- tidyselect::vars_select (treatment_var, 
                                          c( "total_number_of_treatments_across_all_types...228",
                                             "8:_satisfaction_with_healthcare" ,
                                             "9:_satisfaction_results",
                                             "10:_rest_of_life" ))

dat_treatment_var <- dat_sub [, names (dat_sub) %in% treatment_var2]


new.name1 <- c("total_rx_no", "statisfac_healthcare", "statisfac_result", "rest_of_life")

new.name2 <- paste0 ("base_", new.name1)

names(dat_treatment_var) <- new.name2  


```

### Baseline medicine

```{r}


treatment_var2 <- tidyselect::vars_select (treatment_var, 
                                          c( "total_number_of_treatments_across_all_types...228",
                                             "8:_satisfaction_with_healthcare" ,
                                             "9:_satisfaction_results",
                                             "10:_rest_of_life" ))

dat_meds_var <- dat_sub [, names (dat_sub) %in% meds_var]


```

### Baseline demographics

```{r}


misc_var2 <- tidyselect::vars_select (misc_var, 
                                          c( "weight_(kg)",
                                             "height_(cm)"))

dat_misc_var <- dat_sub [, names (dat_sub) %in% misc_var2]


new.name1 <- c("ht", "wt")

new.name2 <- paste0 ("base_", new.name1)

names(dat_misc_var) <- new.name2  
```

### Baseline ses

```{r}


dat_ses_var  <- dat_sub [, names (dat_sub) %in% ses_var]


new.name1 <- c("ses_income", "ses_economic", "ses_occ", "ses_resource", "ses_advantage")

new.name2 <- paste0 ("base_", new.name1)

names(dat_ses_var) <- new.name2  
```

### Baseline symptom history variables

```{r}


symptHx_var2  <- tidyselect::vars_select (symptHx_var, 
                                          c("currently_having_a_flare_up?",
                                            "p&n/n_below__waist_in_past_3_days"))

dat_symptHx_var  <- dat_sub [, names (dat_sub) %in% symptHx_var2]

new.name1 <- c("current_flare", "pnn_below_waist")

new.name2 <- paste0 ("base_", new.name1)

names(dat_symptHx_var) <- new.name2  
```

### Baseline aggravating variables

```{r}
aggr_var2 <-  tidyselect::vars_select (aggr_var, 
                                          -c("done_anything_to_agg?" ,
                                             "agg:_lying_on_back...360",
                                             "agg:_lying_on_stomach...362",
                                             "what_is_most_difficult_about_getting_into_a_car?...370",
                                             "what_is_most_difficult_about__sit_to_stand?",
                                             "what_is_most_difficult_about_getting_into_a_car?...369",
                                             "what_is_most_difficult_about_sit_to_stand?",
                                             "sorer_to_lie_on_one_side_than_the_other?"))

dat_aggr_var  <- dat_sub [, names (dat_sub) %in% aggr_var2]

new.name1 <- c( "walk", "stand", "sitfirm", "sitsoft", "lie_back", "lie_stom", "car", "sts",
               "cough", "bend", "lift")

new.name2 <- paste0 ("base_agg_", new.name1)

names(dat_aggr_var) <- new.name2  
```

### Baseline easing variables

```{r}
ease_var2 <-  tidyselect::vars_select (ease_var, 
                                          -c("most_comfortable_side_to_lie_on?...386" ,
                                             "most_comfortable_side_to_lie_on?...387"  ,
                                             "ease:_lying_sore_side...416",
                                             "ease:_lying_good_side...418",
                                             "assessment:_obs:_standing-increased_lordosis",
                                             "observation:_standing-increased_lordosis",
                                             "decreased_lordosis...446",
                                             "decreased_lordosis...447",
                                             "movement_eases_sympt",
                                             "night_pain+_movement_eases"))

dat_ease_var  <- dat_sub [, names (dat_sub) %in% ease_var2]

new.name1 <- c("stand", "sitfirm", "sitsoft", "walk", "lie_back", "lie_back_bent", "lie_sore", "lie_good", "lie_stom")

new.name2 <- paste0 ("base_ease_", new.name1)

names(dat_ease_var) <- new.name2  
```

### Baseline lumbar curve variables

```{r}
obj_curve_var2 <-  tidyselect::vars_select (obj_curve_var, 
                                          c("observation:_standing-increased_lordosis",
                                             "decreased_lordosis...447" ,
                                             "presence_of_a_list...452",
                                             "list_direction...457" ,
                                            "list_corresponding_to_worst_side" ))

dat_obj_curve_var <- dat_sub [, names (dat_sub) %in% obj_curve_var2]

new.name1 <- c("inc_lord", "dec_lord", "list", "list_dir", "list_dir_side")

new.name2 <- paste0 ("base_", new.name1)

names(dat_obj_curve_var) <- new.name2  
```

### Baseline rom variables

```{r}
obj_rom_var2 <-  tidyselect::vars_select (obj_rom_var, 
                                          c("amt:_flexion_range_(cm)...462",
                                             "amt:_extension_range_(cm)" ,
                                             "amt:_llf_range_(cm)",
                                             "amt:_rlf_range_(cm)"))

dat_obj_rom_var  <- dat_sub [, names (dat_sub) %in% obj_rom_var2]

new.name1 <- c("flex", "ext", "llf", "rlf")

new.name2 <- paste0 ("base_rom_", new.name1)

names(dat_obj_rom_var) <- new.name2  
```

### Baseline core variables

```{r}
obj_core_var2 <-  tidyselect::vars_select (obj_core_var, 
                                          c("core_stability_in_standing" ,
                                             "ta_quality_(lower_threshold)" ,
                                             "ta_hypervig.",
                                             "ta_low_tone"))

dat_obj_core_var <- dat_sub [, names (dat_sub) %in% obj_core_var2]

new.name1 <- c("core", "ta_qual", "ta_hyper", "ta_tone")

new.name2 <- paste0 ("base_", new.name1)

names(dat_obj_core_var) <- new.name2  

```

### Baseline sitting variables

```{r}
obj_sit_var2 <-  tidyselect::vars_select (obj_sit_var, 
                                          c("sitting:_degree_of_flexed_posture...495"  ,
                                             "sitting:_pain_response_to_correction...500"))

dat_obj_sit_var <- dat_sub [, names (dat_sub) %in% obj_sit_var2]

new.name1 <- c("sit_flex", "sit_pain_corr")

new.name2 <- paste0 ("base_", new.name1)

names(dat_obj_sit_var) <- new.name2  

```

### Baseline neuro variables

```{r}
obj_neuro_var2 <-  tidyselect::vars_select (obj_neuro_var, 
                                          c("positive_slr",
                                            "positive_pkb",
                                            "comparable_sensory_deficit...508",
                                            "comparable_myo_deficit...509",
                                            "comparable_knee_jerk_deficit",
                                            "comparable_ankle_jerk_reflex",
                                             "total_comparable_neuro_signs...513",
                                            "clinical_radiculo-_pathy...515",
                                            "clinical_radiculopathy_with_no_mechanical_cause_on_imaging" ))

dat_obj_neuro_var <- dat_sub [, names (dat_sub) %in% obj_neuro_var2]

new.name1 <- c("slr", "pkb", "sens_deficit", "myo_deficit", "knee_jerk_deficit", "ank_jerk_deficit", "total_neuro", "radiculo", "radiculo_image")

new.name2 <- paste0 ("base_", new.name1)

names(dat_obj_neuro_var) <- new.name2  

```

### Baseline aggravating2 variables

```{r}
aggr2_var2 <-  tidyselect::vars_select (aggr2_var, 
                                          c("history_of_heavy_lifting_job_(p25)",
                                            "discogenic_pain" ,
                                            "discogenic_factors",
                                            "repeated_movements:_reducible?"))

dat_aggr2_var <- dat_sub [, names (dat_sub) %in% aggr2_var2]

new.name1 <- c("hx_lift", "disc_pain", "disc_fac", "rep_movt_reduce")

new.name2 <- paste0 ("base_", new.name1)

names(dat_aggr2_var) <- new.name2  

```

### Baseline multifidus variables

```{r}
obj_core2_var2 <-  tidyselect::vars_select (obj_core2_var, 
                                          -c("multifidus_substitution"))

dat_obj_core2_var  <- dat_sub [, names (dat_sub) %in% obj_core2_var2 ]

new.name1 <- c("mf_tone", "mf_qual", "mf_hyper")

new.name2 <- paste0 ("base_", new.name1)

names(dat_obj_core2_var) <- new.name2  

```

### Baseline disc variables

```{r}
obj_disc_var2 <-  tidyselect::vars_select (obj_disc_var, 
                                           c("regular_compression",
                                             "palpation:_comparable_level_of_pain_and/or_stiffness"))

dat_obj_disc_var   <- dat_sub [, names (dat_sub) %in% obj_disc_var2]

new.name1 <- c("reg_compress", "comparable_stiff")

new.name2 <- paste0 ("base_", new.name1)

names(dat_obj_disc_var) <- new.name2  

```

### Baseline redflag variables

```{r}
redflag_var2 <-  tidyselect::vars_select (redflag_var, 
                                           c("general_health_state"))

dat_redflag_var  <- dat_sub [, names (dat_sub) %in% redflag_var2]

new.name1 <- c("gen_health")

new.name2 <- paste0 ("base_", new.name1)

names(dat_redflag_var) <- new.name2  

```

### Baseline euroqol_var variables

```{r}
euroqol_var2 <-  tidyselect::vars_select (euroqol_var, 
                                           c("21:_euroqol:_mobility",
                                             "euroqol:_person_appll_care",
                                             "euroqol:_usual_activities",
                                             "euroqol:_pain/discomfort",
                                             "euroqol:_anxiety/depression",
                                             "euroqol_utility_score_(uk_tto)"))

dat_euroqol_var  <- dat_sub [, names (dat_sub) %in% euroqol_var2]

new.name1 <- c("mobility", "person_care", "activities", "pain", "anx_dep", "utility")

new.name2 <- paste0 ("base_euroq_", new.name1)

names(dat_euroqol_var) <- new.name2  

```


# Create new dataframe

```{r}

df <- bind_cols(dat_id_var,
                dat_misc_var,
                dat_base_var,
                dat_orebro_var,
                dat_wk5_var,
                dat_wk10_var,
                dat_wk26_var,
                dat_wk52_var,
                dat_aggr_var,
                dat_aggr2_var,
                dat_ease_var,
                dat_obj_core2_var,
                dat_obj_core_var,
                dat_obj_curve_var,
                dat_obj_disc_var,
                dat_obj_neuro_var,
                dat_obj_rom_var,
                dat_obj_sit_var,
                dat_redflag_var,
                dat_ses_var,
                dat_sfbs_var,
                dat_symptHx_var,
                dat_symptom_var,
                dat_symptomLoc_var,
                dat_treatment_var,
                dat_episode_var,
                dat_fab_var,
                dat_euroqol_var)

```

# Check class

```{r}
df_chr2num <- df %>%
  dplyr::select_if(is.character) %>%
  dplyr::select (matches ("wk|oreb|rom")) %>%
  mutate_all(as.numeric)

df[names (df_chr2num)] <- df_chr2num

df_class <- map_chr(df, class)

df_num2chr <- df %>%
  dplyr::select_if(is.numeric) %>%
  dplyr::select (-matches ("id|ht|wt|time|osw|lbp|lp|osw|oreb|rom|gen|ses|sfbs|total_rx|fab|euroq|ratio|duration")) %>%
  mutate_all(as.character)

df[names (df_num2chr)] <- df_num2chr


df_chr <- df %>%
  dplyr::select_if(is.character) 

df_num <- df %>%
  dplyr::select_if(is.numeric) 


```


```{r}
tab1 <- tableby (~., data = df, digits = 2, digits.p = 2)

summary (tab1)
```

# Create factor levels

```{r}

df$rx_grp <- tolower(df$rx_grp )
df$rx_subgrp <- tolower(df$rx_subgrp)
df$base_leg_duration <- as.numeric(df$base_leg_duration)
df$base_loc_body_ratio <- as.numeric (df$base_loc_body_ratio)
df$base_pain_side <- tolower(df$base_pain_side)
df$base_core <- ifelse (df$base_core == "nil", NA, df$base_core)
df$base_mf_tone <- ifelse (df$base_mf_tone == "nil", NA, df$base_mf_tone)
df$base_leg_symptom <- ifelse (df$base_leg_symptom == "nil", "no", df$base_leg_symptom)
df$base_list_dir_side <- as.character(df$base_list_dir_side)

df_chr <- df %>%
  dplyr::select_if(is.character) %>%
  mutate_all(as.factor)

levels (df_chr$rx_grp) <- c ("advice", "individualisedphysio")
levels (df_chr$rx_subgrp) <- c ("dhr",  "nrdp", "rdp",  "mfp",  "mtg" )

levels (df_chr$base_agg_walk) <-
  levels (df_chr$base_agg_stand)  <- 
  levels (df_chr$base_agg_sitfirm) <- 
  levels (df_chr$base_agg_sitsoft) <- 
  c("0", "1", "2", "3", "4") # 0 good, 4 bad

levels (df_chr$base_agg_lie_back) <-
  levels (df_chr$base_agg_lie_stom) <- 
  levels (df_chr$base_agg_car) <- 
  levels (df_chr$base_agg_sts) <- 
  levels (df_chr$base_agg_cough) <- 
  levels (df_chr$base_agg_bend) <- 
  levels (df_chr$base_agg_lift) <- 
  c("0", "1", "2", "3", "4", "5") # 0 good, 5 bad

levels (df_chr$base_ease_stand) <-
  levels (df_chr$base_ease_sitfirm) <- 
  levels (df_chr$base_ease_sitsoft) <- 
  levels (df_chr$base_ease_walk) <- 
  levels (df_chr$base_ease_lie_back) <- 
  levels (df_chr$base_ease_lie_back_bent) <- 
  levels (df_chr$base_ease_lie_sore) <-
  levels (df_chr$base_ease_lie_good) <- 
  levels (df_chr$base_ease_lie_stom) <- 
  c("0", "1") # 0 good, 1 bad

levels (df_chr$base_hx_lift) <- 
  levels (df_chr$base_disc_pain) <- 
  levels (df_chr$base_rep_movt_reduce) <- 
  c("0", "1") # 0 yes, 1 no

levels (df_chr$base_disc_fac) <- 
  as.character (c(0:9))


levels (df_chr$base_core) <- 
  c("minimal", "fair", "good" )

levels (df_chr$base_ta_qual) <- 
  levels (df_chr$base_ta_hyper) <- # 0 yes, 1 no
  levels (df_chr$base_ta_tone) <-  # 0 yes, 1 no
  levels (df_chr$base_mf_hyper) <-  # 0 yes, 1 no
  levels (df_chr$base_mf_qual) <-  # 0 yes, 1 no
  c("0", "1") 

levels (df_chr$base_mf_tone) <- c("> 30% MVC", "< 30% MVC")

levels (df_chr$base_inc_lord) <- c("0", "1", "2") # 0 nil, 1 mild, 2 mod

levels (df_chr$base_dec_lord) <- c("0", "1", "2", "3") # 0 nil, 1 mild, 2 mod, 3 marked

levels (df_chr$base_list) <- c("0", "1", "2") # 0 nil, 1 mild, 2 mod

levels (df_chr$base_list_dir) <- c("0", "1", "2") # 0 na, 1 left, 2 right

levels (df_chr$base_reg_compress) <- c("0", "1") # 0 yes, 1 no

levels (df_chr$base_slr) <- 
  levels (df_chr$base_pkb) <- 
  levels (df_chr$base_sens_deficit) <- 
  levels (df_chr$base_myo_deficit)<- 
  levels (df_chr$base_knee_jerk_deficit) <- 
  levels (df_chr$base_ank_jerk_deficit) <- 
  levels (df_chr$base_total_neuro) <- 
  levels (df_chr$base_radiculo) <- 
  levels (df_chr$base_radiculo_image) <- 
  c("0", "1") # 0 yes, 1 no

levels (df_chr$base_sit_flex) <- c("0", "1", "2", "3") # 0 nil, 1 mild, 2 mod, 3 mark

levels (df_chr$base_sit_pain_corr) <- c("0", "1", "2") # 0 improve, 1 same, 2 worse

levels (df_chr$base_current_flare)  <-
  levels (df_chr$base_pnn_below_waist)
  levels (df_chr$base_list_dir_side) <- c("0", "1") # 0 yes, 1 no

levels (df_chr$base_back_leg_relation) <- c("0", "1", "2") # 0 yes, 1 no

levels (df_chr$base_lbp_symptom) <- c("no", "yes")
  
levels (df_chr$base_leg_symptom) <- c("no", " ant thigh", "below knee", "both") # 0 deep, 1 superficial, 2 na # need to check

levels (df_chr$base_freq_symptom) <- c("0", "1", "2") # 0 <50%, 1 >50%, 2 constant

levels (df_chr$base_back_leg_relation) <- c("0", "1", "2") # 0 yes, 1 no, 2 na

levels (df_chr$base_onset_symptom) <- 
  levels (df_chr$base_time_symptom) <- 
  levels (df_chr$base_next_day_symptom) <- c("n_appl", "0", "1", "2", "3") 

levels (df_chr$base_pain_side) <- c("n_appl", "left", "right") 

levels (df_chr$base_loc_antthigh_pain) <- 
  levels (df_chr$base_loc_belowknee_pain) <- 
  levels (df_chr$base_loc_leg_pain) <-
  c("0", "1") # 0 yes, 1 no

levels (df_chr$base_loc_mostpain) <- 
  c("0", "1", "2", "3", "4", "5") # 0 back, 1 buttock, 2 groin, 3 thigh, 4 leg, 5 foot

levels (df_chr$base_statisfac_healthcare) <- 
 levels (df_chr$base_statisfac_result) <- 
 levels (df_chr$base_rest_of_life) <-  c("0", "1", "2", "3", "4") # 0 dissatistied 4 very satisfied

levels (df_chr$base_first_episode) <- c("0", "1") # 0 yes, 1 no

# 0 <1mth , 1 2-6mth, 2 6-12mth, 3 1-2yr, 4 >3yr, 5 na
levels (df_chr$base_first_episode_period) <- c("0", "1", "2", "3", "4", "5")


```



```{r}

df2 <- df %>%
  dplyr::select_if(is.numeric) %>%
  bind_cols(df_chr)


```

```{r}
var_keep1 <- !grepl ("osw_q|ses|sfbs|euroq|statisfac|hyper|total_rx|rest|first|fab", names (df2)) 

df3 <- df2 [, var_keep1 ]

```

# Save cleaned data

```{r}

saveRDS (df3, "output/df_clean.RDS")

xlsx::write.xlsx2 (df3, "output/data_clean.xlsx")

```

# Load cleaned data

```{r}
rm (list = ls())
df <- readRDS("output/df_clean.RDS")
```

# Select important variables

```{r}

df_sub <- df[, grepl ("id|rx_grp|rx_sub|oreb_q|osw|lbp|_lp", names (df))]
df_sub <- df_sub [, !grepl ("pain|dir", names (df_sub))]

```

# Rename orebro variables

- removed question 8 and 15, as I do not feel meaningful. can change

```{r}
# names (df_sub) [grepl ("oreb_q8", names (df_sub))] <-
#   str_replace(names (df_sub) [grepl ("oreb_q8", names (df_sub))], "oreb_q8", "pain_pastwk")

names (df_sub) [grepl ("oreb_q11", names (df_sub))] <- 
  str_replace(names (df_sub) [grepl ("oreb_q11", names (df_sub))], "oreb_q11", "pain_cope_success")

names (df_sub) [grepl ("oreb_q12", names (df_sub))] <- 
  str_replace(names (df_sub) [grepl ("oreb_q12", names (df_sub))], "oreb_q12", "anx")

names (df_sub) [grepl ("oreb_q13", names (df_sub))] <- 
  str_replace(names (df_sub) [grepl ("oreb_q13", names (df_sub))], "oreb_q13", "depress")

names (df_sub) [grepl ("oreb_q14", names (df_sub))] <- 
  str_replace(names (df_sub) [grepl ("oreb_q14", names (df_sub))], "oreb_q14", "pain_persist")

# names (df_sub) [grepl ("oreb_q15", names (df_sub))] <-
#   str_replace(names (df_sub) [grepl ("oreb_q15", names (df_sub))], "oreb_q15", "work_expect")


```

# Recode orebro function

- func = sum of questions 20 to 24
- fear = sum of questions 17 to 19

```{r}
df_sub <- df_sub %>%
  mutate (base_func = base_oreb_q20 + base_oreb_q21 + base_oreb_q22 + base_oreb_q23 ,
          wk5_func =  wk5_oreb_q20 + wk5_oreb_q21 + wk5_oreb_q22 + wk5_oreb_q23 ,
          wk10_func = wk10_oreb_q20 + wk10_oreb_q21 + wk10_oreb_q22 + wk10_oreb_q23 ,
          wk26_func = wk26_oreb_q20 + wk26_oreb_q21 + wk26_oreb_q22 + wk26_oreb_q23 ,
          wk52_func = wk52_oreb_q20 + wk52_oreb_q21 + wk52_oreb_q22 + wk52_oreb_q23,
          base_fear = base_oreb_q17 + base_oreb_q18 + base_oreb_q19,
          wk5_fear = wk5_oreb_q17 + wk5_oreb_q18 + wk5_oreb_q19,
          wk10_fear = wk10_oreb_q17 + wk10_oreb_q18 + wk10_oreb_q19,
          wk26_fear = wk26_oreb_q17 + wk26_oreb_q18 + wk26_oreb_q19,
          wk52_fear = wk52_oreb_q17 + wk52_oreb_q18 + wk52_oreb_q19) %>%
  dplyr::select (-matches ("oreb")) %>%
  dplyr::select (-matches ("func")) %>% # remove this as use oswestry as functional outcome
  dplyr::select (id, rx_grp, rx_subgrp, matches ("base_"), matches ("wk5_"), 
          matches ("wk10_"), matches ("wk26_"), matches ("wk52_"))
          

```


# Check missing

## Check percentage number of missing variables with missing columns

```{r}

missing_per_indv <- (rowSums(is.na(df_sub))/ ncol (df_sub)) * 100 
missing_per_indv

```


### Remove subjects with more than 50% missing columns

```{r}


df_sub2 <- df_sub  [missing_per_indv < 50, ] 

```

# Create a new dataframe of early and late change

early change - week 10 values - baseline values
late change - week 52 values - baseline values

```{r}
const.df <- df_sub2[,!grepl ("base|wk", names(df_sub2))]
base.df <- df_sub2[,grepl ("base_|duration|symptom", names(df_sub2))]
base.df <- base.df[,!grepl ("duration|symptom", names(base.df))]
wk5.df <- df_sub2[,grepl ("wk5_", names(df_sub2))]
wk10.df <- df_sub2[,grepl ("wk10_", names(df_sub2))]
wk26.df <- df_sub2[,grepl ("wk26_", names(df_sub2))]
wk52.df <- df_sub2[,grepl ("wk52_", names(df_sub2))]

wk5_base <- wk5.df - base.df
wk10_base <- wk10.df - base.df
wk26_base <- wk26.df - base.df
wk52_base <- wk52.df - base.df

wk10_wk5 <- wk10.df - wk5.df
wk26_wk5 <- wk26.df - wk5.df
wk52_wk5 <- wk52.df - wk5.df

wk26_wk10 <- wk26.df - wk10.df
wk52_wk10 <- wk52.df - wk10.df

wk52_wk26 <- wk52.df - wk26.df


df.list <- list (wk5_base, 
                 wk10_base,
                 wk26_base,
                 wk52_base,
                 wk10_wk5,
                 wk26_wk5,
                 wk52_wk5,
                 wk26_wk10,
                 wk52_wk10,
                 wk52_wk26)

for (n in seq_along (df.list)){
  
  df.list[[n]] <- df.list[[n]] %>%
       mutate (grp = const.df$rx_grp,
          subgrp = const.df$rx_subgrp,
          id = const.df$id)
}

names (df.list) <- c("wk5_base", 
                     "wk10_base",
                     "wk26_base",
                     "wk52_base",
                     "wk10_wk5",
                     "wk26_wk5",
                     "wk52_wk5",
                     "wk26_wk10",
                     "wk52_wk10",
                     "wk52_wk26")

```

# Save split dataframes

```{r}

saveRDS (df.list, "output/df_change.RDS")

```


