---
title: "3-mediation_late"
author: "bernard-liew"
date: "2020-06-10"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Load library 

```{r message=FALSE, warning=FALSE}

# Helper packages
library (tidyverse)
library (tidyselect)
library (arsenal)
library (janitor)
library (magrittr)
library (Rgraphviz)
library (corrr)

# Import
library(readxl)
library (xlsx)

# Missing data
library (mice)
library (VIM)

# Modelling
library (bnlearn)
library (caret)

# Parallel
library (doParallel)

```

# Introduction

This is a bayesian network analysis where the variables are the change scores between week 52 and baseline.

# Import data

```{r}

rm (list = ls())
df_list <- readRDS("output/df_change.RDS")

```

# Subset data

```{r}
df <- df_list[["wk52_base"]]
names(df)[1:8] <- paste0(str_remove(names(df)[1:8] , "wk52_"), "_late")
```

# Exploratory  analysis

## Between group comparisons

```{r, asis = TRUE}
tableby (subgrp ~., data = df, digits = 2, digits.p = 2) %>%	
  summary () 
```

## Correlation plots

```{r}
df %>%	
     select_if (is.numeric) %>%	
     select(-id) %>%	
     correlate() %>%	
     rearrange() %>%	
     network_plot(colors = c("red", "green"))
```

# BN analysis

## Early change 

### Create blacklist

```{r}

df.bn = as.data.frame (df)
df.bn$id <- NULL
df.bn$subgrp <- NULL # since the earlier descriptives show no difference using ANOVA

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)])

bl1 = tiers2blacklist(tiers_bl)
bl = rbind(bl1)

```

## Create whitelist

```{r}
wl =  matrix(c("grp", "lbp_late"), nrow = 1, ncol = 2, byrow = TRUE, 
              dimnames = list(NULL,c("from", "to"))) 
wl = rbind(wl, 
           c("grp", "lp_late"),
           c("grp", "osw_late")) 
```


### Build BN model

#### Just with blacklist 

```{r}

doParallel::registerDoParallel(7)
n_boot = 200



############

boot_bl <-  foreach (B = 1: n_boot) %dopar%{
    boot.sample = df.bn[sample(nrow(df.bn), 
                                          nrow(df.bn), replace = TRUE), ]
    bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                              maximize.args = list(blacklist = bl))
}
#############


  

```

#### See results

```{r fig.height=10, fig.width=10}

bootstr = custom.strength(boot_bl, nodes = names(df.bn))
avg = averaged.network(bootstr, threshold = 0.5)
fit = bn.fit (avg, df.bn, method = "mle")

g = strength.plot(avg, 
                  bootstr, 
                  shape = "rectangle",
                  main = "Figure")

graph::nodeRenderInfo(g) = list(fontsize=18)


```

#### With blacklist and whitelist

```{r}

doParallel::registerDoParallel(7)
n_boot = 200



############

boot_wl  =  foreach (B = 1: n_boot) %dopar%{
    boot.sample = df.bn[sample(nrow(df.bn), 
                                          nrow(df.bn), replace = TRUE), ]
    bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                              maximize.args = list(blacklist = bl))
}
#############


  

```

### See results

```{r fig.height=10, fig.width=10}

bootstr = custom.strength(boot_bl, nodes = names(df.bn))
avg = averaged.network(bootstr, threshold = 0.5)
fit = bn.fit (avg, df.bn, method = "mle")

g = strength.plot(avg, 
                  bootstr, 
                  shape = "rectangle",
                  highlight = list (arcs = wl), 
                  main = "Figure")

graph::nodeRenderInfo(g) = list(fontsize=18)


```

## Performance evaluation 

### On model with just blacklist

Nested Cross validation. 
Inner is bootstrap resampling for model averaging. 
Outer is 10 fold CV for performance evaluation.

```{r, eval = FALSE}

flds <- flds <- createFolds(1:nrow(df.bn), 
                            k = 10, list = TRUE, returnTrain = TRUE)
n_boot = 200
doParallel::registerDoParallel(7)

corr.df.list <- list()

for (k in seq_along(flds)) {
  
  train <-  df.bn [flds[[k]], ] %>% as.data.frame()
  test <- df.bn [-flds[[k]], ] %>% as.data.frame()
  
  ############
  
  boot  =  foreach (B = 1: n_boot) %dopar%{
      boot.sample = train[sample(nrow(train), 
                                            nrow(train), replace = TRUE), ]
      bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                                maximize.args = list(blacklist = bl,  
                                                     #whitelist = wl.list[[n]],
                                                      k = log(nrow(boot.sample))))
  }
  #############
  
  bootstr <-  custom.strength(boot, nodes = names(train))
  avg <-  averaged.network(bootstr, threshold = 0.5)
  fit <-  bn.fit (avg, train, method = "mle")
  
  imp.list = impute (fit, data = test, method = "bayes-lw")
  inames = names (imp.list) [!names (imp.list) %in% c("grp", "subgrp")]
  corr.df =  structure(numeric(length (inames)), names = inames)
  
  for (var in inames) {
      corr.df[var] = cor(predict(fit, data = imp.list, var, method = "bayes-lw"), 
                         imp.list[, var])
    }
  
  corr.df.list[[k]] <- corr.df
  

}

corr.df <- bind_cols (corr.df.list) %>%
  apply (1, mean)

names (corr.df) <- inames

corr.df

cat ("The mean correlation is:", mean (corr.df))
```


### On model with blacklist and whitelist

Nested Cross validation. 
Inner is bootstrap resampling for model averaging. 
Outer is 10 fold CV for performance evaluation.

```{r, eval = FALSE}

flds <- flds <- createFolds(1:nrow(df.bn), 
                            k = 10, list = TRUE, returnTrain = TRUE)
n_boot = 200
doParallel::registerDoParallel(7)

corr.df.list <- list()

for (k in seq_along(flds)) {
  
  train <-  df.bn [flds[[k]], ] %>% as.data.frame()
  test <- df.bn [-flds[[k]], ] %>% as.data.frame()
  
  ############
  
  boot  =  foreach (B = 1: n_boot) %dopar%{
      boot.sample = train[sample(nrow(train), 
                                            nrow(train), replace = TRUE), ]
      bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                                maximize.args = list(blacklist = bl,  
                                                     whitelist = wl,
                                                      k = log(nrow(boot.sample))))
  }
  #############
  
  bootstr <-  custom.strength(boot, nodes = names(train))
  avg <-  averaged.network(bootstr, threshold = 0.5)
  fit <-  bn.fit (avg, train, method = "mle")
  
  imp.list = impute (fit, data = test, method = "bayes-lw")
  inames = names (imp.list) [!names (imp.list) %in% c("grp", "subgrp")]
  corr.df =  structure(numeric(length (inames)), names = inames)
  
  for (var in inames) {
      corr.df[var] = cor(predict(fit, data = imp.list, var, method = "bayes-lw"), 
                         imp.list[, var])
    }
  
  corr.df.list[[k]] <- corr.df
  

}

corr.df <- bind_cols (corr.df.list) %>%
  apply (1, mean)

names (corr.df) <- inames

corr.df

cat ("The mean correlation is:", mean (corr.df))
```
