---
title: "4-mediation_early2late"
author: "bernard-liew"
date: "2020-07-02"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


# Load library 

```{r message=FALSE, warning=FALSE}

# Helper packages
library (tidyverse)
library (tidyselect)
library (arsenal)
library (janitor)
library (magrittr)
library (Rgraphviz)
library (corrr)
library (corrplot)

# Import
library(readxl)
library (xlsx)

# Missing data
library (mice)
library (VIM)

# Modelling
library (bnlearn)
library (caret)

# Parallel
library (doParallel)

```

# Introduction

This is a bayesian network analysis where the early change variables are between week 10 and baseline. The late change variables are between week 52 and week 10.

# Import data

```{r}

rm (list = ls())
df_list <- readRDS("output/df_change.RDS")

```

# Subset data

```{r}
df1 <- df_list[["wk10_base"]]
names(df1)[grepl("wk", names (df1))] <- paste0(str_remove(names(df1)[grepl("wk", names (df1))], "wk10_"), "_early")

df2 <- df_list[["wk52_wk10"]]
names(df2)[grepl("wk", names (df2))] <- paste0(str_remove(names(df2)[grepl("wk", names (df2))], "wk52_"), "_late")

df3 <- df_list[["wk52"]]
df3 <- df3 %>%
  select (id, grp, subgrp, wk52_lbp, wk52_lp, wk52_osw, wk52_func) 
names(df3)[grepl("wk", names (df3))] <- paste0(str_remove(names(df3)[grepl("wk", names (df3))], "wk52_"), "_outcome")

df <- df1 %>%
  inner_join (df2, by = c("id", "subgrp", "grp")) %>%
  inner_join (df3, by = c("id", "subgrp", "grp")) %>%
  #select (-contains ("func_"))%>%
  rename (disability_early = osw_early,
          disability_late = osw_late,
          disability_outcome = osw_outcome)
```

# Exploratory  analysis

## Between group comparisons

```{r, results = "asis"}
tableby (subgrp ~., data = df, digits = 2, digits.p = 2) %>%	
  summary () 
```

## Correlation plots

```{r}
col<- colorRampPalette(c("red", "white", "blue"))(20)
df %>%	
  select_if (is.numeric) %>%	
  select (-id) %>%
  cor (use = "complete.obs") %>%
  corrplot(type="upper", tl.col="black", tl.srt=45, col=col)

```

# BN analysis

## Early change with func as function, and with absolute outcome

### Create blacklist

```{r}

df.bn = as.data.frame (df)
df.bn[, grepl ( "id|subgrp|func",names (df.bn))] <- NULL

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("early",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)])
bl1 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)])

bl2 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("early",colnames(df.bn), value = TRUE)])

bl3 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("early",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("outcome",colnames(df.bn), value = TRUE)])

bl4 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("outcome",colnames(df.bn), value = TRUE)])

bl5 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("outcome",colnames(df.bn), value = TRUE)])

bl6 = tiers2blacklist(tiers_bl)

bl = rbind(bl1, bl2, bl3, bl4, bl5, bl6)

```



### Build BN model

```{r}

doParallel::registerDoParallel(4)
n_boot <- 200

set.seed (20200420)

############

boot_bl <-  foreach (B = 1: n_boot) %dopar%{
    boot.sample = df.bn[sample(nrow(df.bn), 
                                          nrow(df.bn), replace = TRUE), ]
    bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                              maximize.args = list(blacklist = bl))
}
#############


  

```

### See results

```{r fig.height=10, fig.width=10}

bootstr = custom.strength(boot_bl, nodes = names(df.bn))
avg = averaged.network(bootstr, threshold = 0.5)
fit = bn.fit (avg, df.bn, method = "mle")

g = strength.plot(avg, 
                  bootstr, 
                  shape = "rectangle",
                  main = "Figure")

graph::nodeRenderInfo(g) = list(fontsize=20)
renderGraph(g)


```

## Early change with func as function, with no absolute outcomes

### Create blacklist

```{r}

df.bn = as.data.frame (df)
df.bn[, grepl ( "id|subgrp|outcome|func",names (df.bn))] <- NULL

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("early",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)])
bl1 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)])

bl2 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("early",colnames(df.bn), value = TRUE)])

bl3 = tiers2blacklist(tiers_bl)
bl = rbind(bl1, bl2, bl3)

```



### Build BN model

```{r}

doParallel::registerDoParallel(4)
n_boot <- 200

set.seed (20200420)

############

boot_bl_rel <-  foreach (B = 1: n_boot) %dopar%{
    boot.sample = df.bn[sample(nrow(df.bn), 
                                          nrow(df.bn), replace = TRUE), ]
    bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                              maximize.args = list(blacklist = bl))
}
#############


  

```


# Performance evaluation using nested cross validation. 

Inner is bootstrap resampling for model averaging. 
Outer is bootstrap resampling k = 25 for performance evaluation.

```{r, eval= FALSE}

set.seed (20200420)

flds <- createFolds(1:nrow(df.bn), 
                            k = 10, returnTrain = TRUE)
n_boot = 200
corr.df.list <- list()

for (k in seq_along(flds)) {
  
  train <-  df.bn [flds[[k]], ] %>% as.data.frame()
  test <- df.bn [-flds[[k]], ] %>% as.data.frame()
  
  doParallel::registerDoParallel(4)
  ############
  
  boot  =  foreach (B = 1: n_boot) %dopar%{
      boot.sample = train[sample(nrow(train), 
                                            nrow(train), replace = TRUE), ]
      bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                                maximize.args = list(blacklist = bl))
  }
  #############
  stopImplicitCluster()
  
  bootstr <-  custom.strength(boot, nodes = names(train))
  avg <-  averaged.network(bootstr, threshold = 0.5)
  fit <-  bn.fit (avg, train, method = "mle")
  
  imp.list = impute (fit, data = test, method = "bayes-lw")
  inames = names (imp.list) [!grepl ("grp", names (imp.list))]
  corr.df =  structure(numeric(length (inames)), names = inames)
  
  for (var in inames) {
      corr.df[var] = cor(predict(fit, data = imp.list, var, method = "bayes-lw"), 
                         imp.list[, var])
    }
  
  corr.df.list[[k]] <- corr.df
  

}

corr.df <- bind_cols (corr.df.list) %>%
  apply (1, mean)

names (corr.df) <- inames

corr.df
```

### See results

```{r fig.height=10, fig.width=10}

bootstr = custom.strength(boot_bl_rel, nodes = names(df.bn))
avg = averaged.network(bootstr, threshold = 0.5)
fit = bn.fit (avg, df.bn, method = "mle")

g = strength.plot(avg, 
                  bootstr, 
                  shape = "rectangle",
                  main = "Figure")

graph::nodeRenderInfo(g) = list(fontsize=18)
renderGraph(g)


```

# Save results

```{r}

save (df,
      df.bn,
      bl,
      boot_bl,
      boot_bl_rel,
      bootstr,
      corr.df,
      avg,
      fit,
      file = "output/results_early2late.RData")


```

