---
title: "5-mediation_early2laterr"
author: "bernard-liew"
date: "2020-07-06"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


# Load library 

```{r message=FALSE, warning=FALSE}

# Helper packages
library (tidyverse)
library (tidyselect)
library (arsenal)
library (janitor)
library (magrittr)
library (Rgraphviz)
library (corrr)

# Import
library(readxl)
library (xlsx)

# Missing data
library (mice)
library (VIM)

# Modelling
library (bnlearn)
library (caret)

# Parallel
library (doParallel)

```

# Introduction

This is a bayesian network analysis where the early change variables are between week 10 and baseline. The late change variables are between week 52 and week 26.

# Import data

```{r}

rm (list = ls())
df_list <- readRDS("output/df_change.RDS")

```

# Subset data

```{r}
df1 <- df_list[["wk10_base"]]
names(df1)[1:8] <- paste0(str_remove(names(df1)[1:8] , "wk10_"), "_early")

df2 <- df_list[["wk52_wk26"]]
names(df2)[1:8] <- paste0(str_remove(names(df2)[1:8] , "wk52_"), "_late")

df <- bind_cols(df1, df2) %>%
  select (-c(grp1, subgrp1, id1))

```

# Exploratory  analysis

## Between group comparisons

```{r, results = "asis"}
tableby (subgrp ~., data = df, digits = 2, digits.p = 2) %>%	
  summary () 
```

## Correlation plots

```{r}
df %>%	
     select_if (is.numeric) %>%	
     select(-id) %>%	
     correlate() %>%	
     rearrange() %>%	
     network_plot(colors = c("red", "green"))
```

# BN analysis

## Early change 

### Create blacklist

```{r}

df.bn = as.data.frame (df)
df.bn$id <- NULL
df.bn$subgrp <- NULL # since the earlier descriptives show no difference using ANOVA

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("early",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)])
bl1 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("late",colnames(df.bn), value = TRUE)])

bl2 = tiers2blacklist(tiers_bl)

tiers_bl = list (colnames (df.bn)[colnames(df.bn) %in% grep ("grp",colnames(df.bn), value = TRUE)], 
                 colnames (df.bn)[colnames(df.bn) %in% grep ("early",colnames(df.bn), value = TRUE)])

bl3 = tiers2blacklist(tiers_bl)
bl = rbind(bl1, bl2, bl3)

```



### Build BN model

#### Just with blacklist 

```{r}

doParallel::registerDoParallel(4)
n_boot = 200



############

boot_bl <-  foreach (B = 1: n_boot) %dopar%{
    boot.sample = df.bn[sample(nrow(df.bn), 
                                          nrow(df.bn), replace = TRUE), ]
    bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 3,
                              maximize.args = list(blacklist = bl))
}
#############


  

```

#### See results

```{r fig.height=10, fig.width=10}

bootstr = custom.strength(boot_bl, nodes = names(df.bn))
avg = averaged.network(bootstr, threshold = 0.5)
fit = bn.fit (avg, df.bn, method = "mle")

g = strength.plot(avg, 
                  bootstr, 
                  shape = "rectangle",
                  main = "Figure")

graph::nodeRenderInfo(g) = list(fontsize=18)


```

