---
title: "6-report"
author: "Bernard"
date: "2020-07-02"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Load library 

```{r message=FALSE, warning=FALSE}

# Helper packages
library (tidyverse)
library (Rgraphviz)
library (corrr)
library (corrplot)
library (DataExplorer)
library (cowplot)

# Modelling
library (bnlearn)
library (qgraph)

# Parallel
library (doParallel)

# Tables
library (flextable)
library (officer)


```


# Import data

```{r}

rm (list = ls())

load ("output/results_early2late.RData")

imp.data = impute (fit, data = df.bn, method = "bayes-lw")

var_order <- c("disability_early", "lbp_early", "lp_early", "pain_cope_early", 
               "sleep_early", "work_expect_early", "pain_persist_early", 
               "anx_early", "depress_early","fear_early",
               "disability_late", "lbp_late", "lp_late", "pain_cope_late", 
               "sleep_late", "work_expect_late", "pain_persist_late", 
               "anx_late", "depress_late","fear_late")

```


# Descriptive plot

## Mean & SD

```{r}
df.plot <- df %>%
  pivot_longer(cols = -c("id", "grp", "subgrp"),
               names_to = "var",
               values_to = "val") %>%
  filter (var %in% var_order) %>%
  mutate (var = factor (var, levels = var_order),
          grp = factor (grp, labels = c("Advice", "IndvPT"))) %>%
  group_by(grp, var) %>%
  summarize (Mean = mean (val, na.rm = TRUE),
             Sd = sd (val, na.rm = TRUE))


f <- ggplot (df.plot) +
  geom_point(aes (x = grp, y = Mean), colour = "black", fill = "black", stat = "identity") +
  geom_errorbar(aes (x = grp, ymin = Mean - Sd, ymax = Mean + Sd), width = 0) +
  facet_wrap(~ var, scales = "free") +
  labs (x = "Group",
        y = "Mean difference (SD)") +
  theme(text = element_text(size=16)) +
  theme_cowplot()

tiff(width = 10, height = 8, units = "in", res = 100, file = "../manuscript/fig1.tiff")
f
dev.off()

```

## Plot missing data of subset data

```{r, results="asis"}

f <- plot_missing(df.bn) +
  labs (y = "Percentage missing",
        x = "Variables") +
  theme_cowplot()

tiff(width = 10, height = 8, units = "in", res = 300, file = "../manuscript/sm_fig1.tiff")
f
dev.off()

```

## Correlation 

```{r}
col<- colorRampPalette(c("red", "white", "blue"))(20)

tiff(width = 15, height = 15, units = "in", res = 100, file = "../manuscript/sm_fig2.tiff")
df.bn %>%	
  select_if (is.numeric) %>%	
  cor (use = "complete.obs") %>%
  corrplot(type="upper", tl.col="black", tl.srt=45, col=col, method = "number")
dev.off()

```


# BN Results

```{r fig.height=10, fig.width=10}

demo.var <- c("grp")
# out.var <- grep ("outcome", names (df.bn), value = TRUE)
early.var <-  grep ("early", names (df.bn), value = TRUE)
late.var <-  grep ("late", names (df.bn), value = TRUE)

bootstr = custom.strength(boot_bl_rel, nodes = names(df.bn))
avg = averaged.network(bootstr, threshold = 0.5)
fit = bn.fit (avg, df.bn, method = "mle")

g = strength.plot(avg, 
                  bootstr, 
                  shape = "rectangle")

graph::nodeRenderInfo(g) = list(fontsize=18)
renderGraph(g)

arc_col <- data.frame(arcs = names (edgeRenderInfo(g)$col)) %>%
  separate(arcs, c("parent", "child"), sep = "~")

coef_fit <- coef(fit) 
coef_fit <- coef_fit[!map_lgl(coef_fit, is.matrix)]
coef_fit <- coef_fit[!map_lgl(coef_fit, is.table)]
coef_fit <-  coef_fit %>%
  unlist ()
coef_fit <- coef_fit[!grepl ("Intercept", names (coef_fit))]

coef_fit <- data.frame(arcs = names (coef_fit), coefs = coef_fit) %>%
  separate(arcs, c ("child", "parent"), sep = "[.]") 

new_col <- arc_col %>%
  left_join(coef_fit, by = c("parent", "child")) %>%
  mutate (coefs = replace_na(coefs,88)) %>%
  mutate (col = ifelse (coefs < 0, "red", 
                        ifelse (coefs == 88, "black", "blue"))) %>%
  mutate (col = ifelse (parent == "pain_persist_early" & child == "pain_cope_early", "blue",
                        ifelse (parent == "lbp_early" & child == "pain_cope_early", "blue", col)))

new_arc_col <- new_col$col
names (new_arc_col) <-   names (edgeRenderInfo(g)$col)

nodeRenderInfo(g)$fill[demo.var] = "cornsilk"
nodeRenderInfo(g)$fill[early.var] = "tan1"
nodeRenderInfo(g)$fill[late.var] = "gold"
#nodeRenderInfo(g)$fill[out.var] = "tomato"
edgeRenderInfo(g)$col <- new_arc_col
graph::nodeRenderInfo(g) = list(fontsize=14)


renderGraph(g)

tiff(width = 25, height = 15, units = "in", res = 300, file = "../manuscript/fig2.tiff")
renderGraph(g)
dev.off()

```


# Correlation performance table

```{r}

corr.df_ord <- corr.df[var_order] 
correlation <- data.frame(Variable = names (corr.df_ord),
                          Value = corr.df_ord %>% round (2)) %>%
  mutate (Strength = ifelse (abs (Value) <= 0.3, "negligible",
                             ifelse (abs(Value) > 0.3 & abs(Value <= 0.5), "low",
                                     ifelse (abs(Value) > 0.5 & abs(Value <= 0.7), "moderate",
                                             ifelse (abs(Value) > 0.7 & abs(Value <= 0.9), "high",
                                                     "very high")))))

ft <- flextable(correlation) %>%
      set_caption(paste0("Correlation between observed and predicted change values")) %>%
      autofit()

my_path <- paste0("../manuscript/table1_corr.docx")

my_doc <- read_docx()  %>% 
  body_add_flextable(ft)

print (my_doc, target = my_path)

```


# Probing the expert system BN model

## Network importance

```{r}
net <- qgraph(avg)

net.c <- centralityTable (net,standardized = TRUE,  relative = FALSE)

net.c %>%
  filter (measure %in% c("Betweenness")) %>%
  mutate (node = factor (node, levels = c("grp", var_order))) %>%
  ggplot (aes (x = node, y = value)) +
  geom_point () +
  geom_line (aes (group = 1)) +
  coord_flip()

```
### Evaluating the correlation between `lbp_early`-`lbp_late` relationship

#### See the correlation

```{r fig.height=10, fig.width=10}
set.seed(123)

sim <- cpdist(fit, nodes = c("lbp_early", "lbp_late"), n = 10^4,
               evidence = (TRUE))

m <- lm(lbp_late ~ lbp_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

eqn <- bquote(italic(lbp_late) == .(b0) + .(b1)*italic(lbp_early) * "," ~~ 
                  r^2 == .(r2))

tiff(width = 10, height = 8, units = "in", res = 300, file = "../manuscript/fig3.tiff")

 plot(sim$lbp_early, sim$lbp_late, 
      ylab = "Late change LBP", xlab = "Early change LBP", col = "grey", cex.axis = 1.5, cex.lab = 1.5) + 
  abline(coef(m), lwd = 2) +
  abline(v = 0, col = 2, lty = 2, lwd = 2) +
  abline(h = 0, col = 2, lty = 2, lwd = 2) +
  text(x = -5, y = 5, labels = eqn, cex = 1.2)
 
dev.off()

```

### Evaluating the mediating infuence of `disability_early`  on the `grp`-`lbp_early` relationship

#### Influence of `grp` on `lbp_early`

```{r fig.height=10, fig.width=10}

set.seed(123)

sim <- cpdist(fit, nodes = c("grp", "lbp_early"), n = 10^4,
               evidence = TRUE) # individualisedphysio, advice

m <- lm(lbp_early ~ grp, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

eqn <- bquote(italic(lp_outcome) == .(b0) + .(b1)*italic(lp_late) * "," ~~ 
                  r^2 == .(r2))


sim %>%
  mutate (grp = ifelse (grp == "advice", "Advice", "IndPT")) %>%
  group_by(grp) %>%
  summarize (Mean = mean (lbp_early),
             Sd = sd (lbp_early))  %>%
  ggplot () +
  geom_bar(aes (x = grp, y = Mean), color = "black", stat = "identity") + 
  geom_errorbar(aes (x = grp, ymin = Mean - Sd, ymax = Mean ), width = 0.2) + 
  labs (x = "Group",
        y = "Change in early LBP") + 
  theme_cowplot()


```


#### Influence of `grp` on `lbp_early` when `disability_early` is constant

```{r echo=TRUE, message=FALSE, warning=FALSE}

set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(disability_early = 0))

fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$disability_early = list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fitted.mutilated, nodes = c("grp", "lbp_early"), n = 10^4,
               evidence = TRUE) # individualisedphysio, advice

m <- lm(lbp_early ~ grp, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)


sim %>%
  mutate (grp = ifelse (grp == "advice", "Advice", "IndPT")) %>%
  group_by(grp) %>%
  summarize (Mean = mean (lbp_early),
             Sd = sd (lbp_early))  %>%
  ggplot () +
  geom_bar(aes (x = grp, y = Mean), color = "black", stat = "identity") + 
  geom_errorbar(aes (x = grp, ymin = Mean - Sd, ymax = Mean ), width = 0.2) + 
  labs (x = "Group",
        y = "Change in early LBP") + 
  theme_cowplot()



```

### Evaluating the `disability_early`-`depress_early` relationship

#### See the correlation

```{r fig.height=10, fig.width=10}
set.seed(123)

sim <- cpdist(fit, nodes = c("disability_early", "depress_early"), n = 10^4,
               evidence = (TRUE))

m <- lm(depress_early ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

eqn <- bquote(italic(depress_early) == .(b0) + .(b1)*italic(disability_early) * "," ~~ 
                  r^2 == .(r2))

tiff(width = 10, height = 8, units = "in", res = 300, file = "../manuscript/fig4.tiff")

 plot(sim$disability_early, sim$depress_early, ylab = "Early change depression", xlab = "Early change disability", col = "grey", cex.axis = 1.5, cex.lab = 1.5) + 
  abline(coef(m), lwd = 2) +
  abline(v = 0, col = 2, lty = 2, lwd = 2) +
  abline(h = 0, col = 2, lty = 2, lwd = 2) +
  text(x = -20, y = 6, labels = eqn, cex = 1.2)
 
dev.off()

```

#### Mediating influence of `fear_early`.

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(fear_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$fear_early= list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fitted.mutilated, nodes = c("disability_early", "depress_early"), n = 10^4,
               evidence = (TRUE))

m <- lm(depress_early ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

```

#### Mediating influence of `lbp_early`.

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(lbp_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$lbp_early = list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fitted.mutilated, nodes = c("disability_early", "depress_early"), n = 10^4,
               evidence = (TRUE))

m <- lm(depress_early ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

```

#### Mediating influence of `pain_persist_early`.

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(pain_persist_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$pain_persist_early = list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fitted.mutilated, nodes = c("disability_early", "depress_early"), n = 10^4,
               evidence = (TRUE))

m <- lm(depress_early ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)


```

#### Mediating influence of `fear_early`, `lbp_early`,  `pain_persist_early`

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(fear_early = 0, lbp_early = 0,  pain_persist_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$fear_early = list(coef = c("(Intercept)" = 0), sd = 0)
fitted.mutilated$lbp_early = list(coef = c("(Intercept)" = 0), sd = 0)
fitted.mutilated$pain_persist_early = list(coef = c("(Intercept)" = 0), sd = 0)


g = strength.plot(avg.mutilated, 
                  bootstr, 
                  shape = "rectangle")
graph::nodeRenderInfo(g) = list(fontsize=18)
renderGraph(g)

sim <- cpdist(fitted.mutilated, nodes = c("disability_early", "depress_early"), n = 10^4,
               evidence = (TRUE))

m <- lm(depress_early ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)


```


### Evaluating the `disability_early`-`lp_late` relationship

#### See the correlation

```{r fig.height=10, fig.width=10}
set.seed(123)

sim <- cpdist(fit, nodes = c("disability_early", "lp_late"), n = 10^4,
               evidence = (TRUE))

m <- lm(lp_late ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

eqn <- bquote(italic(lp_late) == .(b0) + .(b1)*italic(disability_early) * "," ~~ 
                  r^2 == .(r2))

tiff(width = 10, height = 8, units = "in", res = 300, file = "../manuscript/fig4.tiff")

 plot(sim$disability_early, sim$depress_late, 
      ylab = "Late change leg pain", xlab = "Early change disability", col = "grey", cex.axis = 1.5, cex.lab = 1.5) + 
  abline(coef(m), lwd = 2) +
  abline(v = 0, col = 2, lty = 2, lwd = 2) +
  abline(h = 0, col = 2, lty = 2, lwd = 2) +
  text(x = 15, y = 75, labels = eqn, cex = 1.2)
 
dev.off()

```

#### Mediating influence of `disability_late`.

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(disability_late = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$disability_late = list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fitted.mutilated, nodes = c("disability_early", "depress_late"), n = 10^4,
               evidence = (TRUE))

m <- lm(depress_late ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)


```

#### Mediating influence of `lbp_early`.

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(lbp_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$lbp_early = list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fit, nodes = c("disability_early", "lp_late"), n = 10^4,
               evidence = (TRUE))

m <- lm(lp_late ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

eqn <- bquote(italic(lp_late) == .(b0) + .(b1)*italic(disability_early) * "," ~~ 
                  r^2 == .(r2))

```

#### Mediating influence of `lp_early`.

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(lp_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$lp_early = list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fit, nodes = c("disability_early", "lp_late"), n = 10^4,
               evidence = (TRUE))

m <- lm(lp_late ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

eqn <- bquote(italic(lp_late) == .(b0) + .(b1)*italic(disability_early) * "," ~~ 
                  r^2 == .(r2))

```

#### Mediating influence of `sleep_early`.

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(sleep_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$sleep_early = list(coef = c("(Intercept)" = 0), sd = 0)

sim <- cpdist(fit, nodes = c("disability_early", "lp_late"), n = 10^4,
               evidence = (TRUE))

m <- lm(lp_late ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

eqn <- bquote(italic(lp_late) == .(b0) + .(b1)*italic(disability_early) * "," ~~ 
                  r^2 == .(r2))

```

#### Mediating influence of `lbp_early`, `sleep_early`, `disability_late`, `lp_early`

```{r fig.height=10, fig.width=10}
set.seed(123)

avg.mutilated = mutilated(avg, evidence = list(lbp_early = 0, sleep_early = 0,disability_late = 0, lp_early = 0))
fitted.mutilated = bn.fit (avg.mutilated , df.bn, method = "mle")
fitted.mutilated$disability_late = list(coef = c("(Intercept)" = 0), sd = 0)
fitted.mutilated$lbp_early = list(coef = c("(Intercept)" = 0), sd = 0)
fitted.mutilated$sleep_early  = list(coef = c("(Intercept)" = 0), sd = 0)
fitted.mutilated$lp_early  = list(coef = c("(Intercept)" = 0), sd = 0)

g = strength.plot(avg.mutilated, 
                  bootstr, 
                  shape = "rectangle")
graph::nodeRenderInfo(g) = list(fontsize=18)
renderGraph(g)

sim <- cpdist(fitted.mutilated, nodes = c("disability_early", "lp_late"), n = 10^4,
               evidence = (TRUE))

m <- lm(depress_late ~ disability_early, data = sim)

coefs <- coef(m) 
b0 <- round(coefs[1], 2)
b1 <- round(coefs[2],2)
r2 <- round(summary(m)$r.squared, 2)
summary (m)

```
